Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-18 proposal/mprop.tex
Add reference to Brooks' mythical man month

Software engineering, compared to other engineering fields, such as
mechanical or electrical engineering, is much more abstract - while 
performing maintenance on a car engine or on an electric panel,
you can actually touch the components, they are physical. However, in
computer science and the engineering of software, you cannot see the whole picture.
Of course one can actually open up a laptop or PC and see and touch the
components, but the software, what is actually displayed to the user, 
is a multitude of layers on top of each other: it starts with a number of characters in some file;
then, that file gets compiled or interpreted to machine
code by other components which run on the operating system; then, these components
can communicate with the kernel (i.e. the component that sits exactly
between the OS and the hardware) and eventually perform the final step - send 
different 1s and 0s encoded into electrical signals to the CPU and various
other hardware components.

>>>>

Software engineering, compared to other engineering fields, such as
mechanical or electrical engineering, is much more abstract \citep{brooks1995mythical}- while 
performing maintenance on a car engine or on an electric panel,
you can actually touch the components, they are physical. However, in
computer science and the engineering of software, you cannot see the whole picture.
Of course one can actually open up a laptop or PC and see and touch the
components, but the software, what is actually displayed to the user, 
is a multitude of layers on top of each other: it starts with a number of characters in some file;
then, that file gets compiled or interpreted to machine
code by other components which run on the operating system; then, these components
can communicate with the kernel (i.e. the component that sits exactly
between the OS and the hardware) and eventually perform the final step - send 
different 1s and 0s encoded into electrical signals to the CPU and various
other hardware components.
